Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-06-23 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
filled out first portion of results section

		\caption{Emission measure distributions for waiting-times $t_N=250,750,1500,2500,3750,5000$ s in the single-fluid case. The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green). The dotted lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution.}

@@

	\par We look first at the $\mathrm{EM}(T)$ for the single-fluid case, \autoref{fig:single_em}. Looking at all six panels, we note that as $t_N$ increases, $\mathrm{EM}(T)$ widens towards both cooler and hotter temperatures. $\mathrm{EM}(T)$ extends toward cooler temperatures because as $t_N$ increases and there is more time between successive heating events, the loop is allowed more time to cool both by radiation and enthalpy flux. $\mathrm{EM}(T)$ extends towards hotter temperatures for similar, but more subtle reasons. As $t_N\to0$, we approach the steady heating case in which conductive and radiative cooling exactly balance the heating. As $t_N$ increases and becomes comparable to and greater than a cooling time, the loop beceomes increasingly tenuous at the time of the subsequent heating event, allowing the loop to reach much hotter temperatures as radiative cooling is very inefficient at low densities. In this way, $\mathrm{EM}(T)$ can ``see'' this greater range of temperatures, both hot and cool, provided it is allowed to undergo a typical heating and cooling cycle. The more curtailed this cycle is by continued reheatings, the more narrow $\mathrm{EM}(T)$ will be.

@@

	\par\hl{Describe differences between different heating function types} Looking at the different curves in each panel of \autoref{fig:single_em}, it is important to note that, although all widen as $t_N$, the way each extends higher and lower temperatures is very different. 

@@

	\par\hl{Address electron and ion cases and how they differ from the single-fluid case in the ways discussed above.}

@@

	\par\hl{Describe differences between IEQ and NEI solutions.}
	%%%%%%%%%%%%%

@@

		\includegraphics[width=2\columnwidth]{figures/nT_sample_curves_tn1500_electron.pdf}
		\caption{Example temperature and density profiles for an intermediate heating frequency, $t_N=1500$ s for several different heating function types.}

@@

	\par\hl{Mostly discussing differences between power-law and uniform on hot side and scaling/non-scaling on the cool side. Lead into this paragraph from the previous paragraph}

>>>>

		\caption{Emission measure distributions for waiting-times $t_N=250,750,1500,2500,3750,5000$ s in the single-fluid case. The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green). The solid lines in the power-law cases show the mean $\mathrm{EM}(T)$ over $N_R$ runs and the shading indicates one standard deviation from the mean. The dashed lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution.}

@@

	\par We look first at $\mathrm{EM}(T)$ for the single-fluid case, \autoref{fig:single_em}. Looking at all six panels, we note that as $t_N$ increases, $\mathrm{EM}(T)$ widens, extending to both cooler ($<4$ MK) and hotter ($>4$ MK) temperatures. $\mathrm{EM}(T)$ extends toward cooler temperatures because as $t_N$ increases and there is more time between successive heating events, the loop is allowed more time to cool both by radiation and enthalpy-driven cooling. $\mathrm{EM}(T)$ extends towards hotter temperatures for similar, but more subtle reasons. As $t_N\to0$, we approach the steady heating case in which conductive and radiative cooling exactly balance the heating. As $t_N$ increases and becomes comparable to and greater than a cooling time, the loop beceomes increasingly tenuous at the time of the subsequent heating event, allowing the loop to reach much hotter temperatures since radiative cooling is very inefficient at low densities and the heat flux saturates. In this way, $\mathrm{EM}(T)$ can ``see'' this greater range of temperatures, both hot and cool, provided it is allowed to undergo a typical heating and cooling cycle. The more curtailed this cycle is by continued reheatings, the more narrow $\mathrm{EM}(T)$ will be.

@@

	\par Looking at the different curves in each panel of \autoref{fig:single_em}, it is important to note that, although $\mathrm{EM}(T)$ for all three types of heating functions widen with increasing wait time, their dependence on $t_N$ is quite different. The uniform (red) and power-law (blue) $\mathrm{EM}(T)$ curves evolve similarly as they extend to cooler temperatures with increasing $t_N$ while the power-law, $\beta=1$ curve (green) extends to cooler temperatures much more rapidly. For example, at $t_N=1500$ s, both the uniform and power-law cases show little to no emission below 2 MK while the $\beta=1$ cases extends to temperatures well below 1 MK. Contrastingly, on the hot side, the power-law and $\beta=1$ curves evolve nearly identically with increasing $t_N$ while the unfiorm heating case shows a cutoff at much lower temperatures, particularly for $t_N\le2500$ s. 

@@

	\par The $\mathrm{EM}(T)$ curves for the different types of heating functions shown in \autoref{fig:el_em}, in which only the electrons are heated, evolve similarly to those shown in \autoref{fig:single_em}. This is particularly true on the cool side where the density is sufficiently high, allowing the electrons and the ions to equilibrate such that there is no discernible difference compared to the single-fluid case. On the hot side, for $t_N\le750$ s, the electron and single-fluid cases are quite similar. However, for $t_N\ge1500$ s, $\mathrm{EM}(T)$ steepens just above 4 MK and then flattens out near 10 MK. This change in shape is most obvious in the uniform heating case where a distinct ``hot shoulder'' forms just above 10 MK. In the power-law cases, this feature is less pronounced and the $\mathrm{EM}(T)$ extends to slightly higher temperatures.

@@

	\par In \autoref{fig:ion_em} in which only the ions are heated, the cool side of the $\mathrm{EM}(T)$ is very similar to both the single-fluid and electron heating cases because the electron and ion populations are in equilibrium during this portion of the loop's evolution. On the hot side, for intermediate to low heating frequencies (i.e. $t_N\ge1500$ s), the $\mathrm{EM}(T)$ in the uniform heating case is truncated below 10 MK and in the power-law cases extends to just above 10 MK for the lowest heating frequency ($t_N=5000$ s). This cutoff at lower temperatures is due to the fact that electrons cannot ``see'' the ions until they have cooled well below their peak temperature. This is discussed in \citetalias{barnes_inference_2016} though in the single-pulse cases, the cutoff occured at lower temperatures. Additionally, in both the uniform and power-law cases, the peak of the $\mathrm{EM}(T)$ is wider for these low frequencies compared to those cases shown in \autoref{fig:single_em} and \autoref{fig:el_em}.
	\par The dashed lines in the panels of \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} show the corresponding $\mathrm{EM}(T_{eff})$ for each heating function type. Only the mean $\mathrm{EM}(T_{eff})$ over $N_R$ runs is shown for these results. In all three figures, for the intermediate to high frequencies (i.e. $t_N\le1500$ s), there is no discernible difference between $\mathrm{EM}(T)$ and $\mathrm{EM}(T_{eff})$. Furthermore, both of the power-law cases show little deviation from ionization equilibrium in the emission measure for even the lowest heating frequencies in the single-fluid, electron heating, and ion heating cases. For $t_N\ge2500$ s in the uniform heating case, in both \autoref{fig:single_em} and \autoref{fig:el_em}, $\mathrm{EM}(T_{eff})$ is truncated at slightly lower temperatures as compared to $\mathrm{EM}(T)$. This hot emission is relocated to cooler temperatures, resulting in a ``bump'' in the emission measure distribution near 10 MK. None of the panels of \autoref{fig:ion_em} show any significant difference between $\mathrm{EM}(T)$ and $\mathrm{EM}(T_{eff})$. This is because the electrons are essentially heated on a timescale dictated by the Coulomb collision frequency which is slow enough to ensure ionization equilibrium during the entire heating phase.

@@

		\includegraphics[width=2\columnwidth]{figures/nT_sample_curves_tn2500_electron.pdf}
		\caption{Example heating (top), temperature (middle), and density (bottom) profiles for an intermediate heating frequency, $t_N=2500$ s for uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green).}

@@

	\par\hl{Mostly discussing differences between power-law and uniform on hot side and scaling/non-scaling on the cool side. Lead into this paragraph from the previous paragraph. Questions to answer: why do power-law cases extend to hotter temperatures for equivalent $t_N$? Why do power-law cases show little to no deviation from IEQ?}
